INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-10-27 chapters/language_definition.tex
little more progress

The key idea of this approach is to avoid all the intermediary layers (nodes) in the syntax tree by considering just the leaf nodes.

@@

\todo{Shortcut approach differs in the way references to children (parser rules) are created.}
\todo{The main/key difference between these two lies in the way we create children fields for parser rules and in the way we are going to link them together using interface concepts.}

The key idea of this approach is to identify rules and nodes that are at the end of the (derivation, inheritance) chain

We call such \emph{end rules} and \emph{end nodes}, respectively, because they cannot transparently break into more rules/nodes.

@@

>>>>

The key idea of this approach is to skip all the intermediary layers (nodes) in the syntax tree and consider just the leaf nodes.

@@

@@

We call the leaf nodes as \emph{end nodes} and \emph{end rules}, respectively, because they cannot transparently break into more rules/nodes.
